This section presents the numerical simulations of the stochastic and deterministic differential models for RSV from the articles and from our own simulations. We aimed to replicate the results of the  article and build our own implementation using the popular language python instead of Matlab. The aim of the authors was to explore how small variations of the birth and RSV transmission rates can affect the RSV dynamics in the population and see the main consequences on the infected I(t).
The deterministic ordinary differential equations (ODEs) are solved with ode45 by the authors and with \textit{solve\_ivp} in our implementation. The stochastic differential equation (SDEs) systems are solved using Euler-Maruyama and Milstein methods. We only implemented our version of the Euler-Maruyama, since the Milstein method, both in the authors and our results, didn't show substantial differences.
After a brief part about the deterministic simulation  the authors concentrate on two different stochastic scenarios. The first one considers the stochastic fluctuations of the birth rate parameter shown by the system of SDEs \ref{eq:System2}. The second scenario considers the stochastic fluctuations of the transmission rate parameter implemented in system \ref{eq:System3}. The authors have employed Monte Carlo techniques to calculate statistical measures such as mean and confidence intervals shown in the graphs. However, the specific details regarding the implementation of this technique have not been explicitly provided by the authors themselves.